The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-03 paper/paper.qmd
update paper

In recent years, the quality and reliability of data collected through social surveys have garnered increasing attention, especially considering how various forms of disruption may influence respondents’ behavior and, subsequently, the quality of survey responses. Social surveys are indispensable tools for obtaining observations into societal trends, guiding public policy, and informing evidence-based decision-making. Thus, ensuring the robustness of data collected from these surveys has implications for the accuracy of the conclusions drawn and for the effective formulation of policy measures. Previous research has made significant strides in understanding factors that impact survey data quality. For example, Groves et al. [@groves2011survey].investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics. Similarly, Couper and de Leeuw [@massey2013we].explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues. In another significant contribution, Fowler and Mangione [@aquilino1993effects]. analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity. Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored. Addressing this gap is paramount to improving the reliability of survey data, particularly in settings where such disruptions are unavoidable.

@@

- **arrow** [@arrow].: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.

- **knitr** [@knitr].: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.

- **rstanarm** [@rstanarm].: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.

@@

-   $\beta_6$: The coefficient for **non_relative interference**, indicating whether interference was caused by non-relatives.

>>>>

In recent years, the quality and reliability of data collected through social surveys have garnered increasing attention, especially considering how various forms of disruption may influence respondents’ behavior and, subsequently, the quality of survey responses. Social surveys are indispensable tools for obtaining observations into societal trends, guiding public policy, and informing evidence-based decision-making. Thus, ensuring the robustness of data collected from these surveys has implications for the accuracy of the conclusions drawn and for the effective formulation of policy measures. Previous research has made significant strides in understanding factors that impact survey data quality. For example, Groves et al. [@groves2011survey]investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics. Similarly, Couper and de Leeuw [@massey2013we]explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues. In another significant contribution, Fowler and Mangione [@aquilino1993effects]analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity. Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored. Addressing this gap is paramount to improving the reliability of survey data, particularly in settings where such disruptions are unavoidable.

@@

- **arrow** [@arrow]: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.

- **knitr** [@knitr]: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.

- **rstanarm** [@rstanarm]: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.

@@

-   $\beta_6$: The coefficient for **non relative interference**, indicating whether interference was caused by non-relatives.
